Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-11-19 Report/convergence_centralized.tex
updated

Using the arguments in Appendices \ref{b_obj} and \ref{mcity}, we can show that the sequence of objective values \eqn{\{f(\ma^t)\}} generated by the iterative algorithm converges \cite[Prop. A.3]{bertsekas1999nonlinear}. Unfortunately, such a claim cannot be made on the convergence of \eqn{\{\ma^t\}}. However, due to the compactness of feasible set, the sequence of iterates \eqn{\{\ma^t\}} is bounded. Therefore, there exists at least one subsequence that converges to a limit point in the feasible set \cite[Th. 3.6]{rudin1964principles}.

We now show that every limit point of the sequence \eqn{\{\ma^t\}} is a stationary point, \textit{i.e.,} the limit point of every convergent subsequence is a stationary point. To do this, let us consider a subsequence \eqn{\{\ma^{t_j} |j = 0,1,\dotsc\}} of \eqn{\{\ma^t\}} that converges to \eqn{\bar{\ma}}, where \eqn{\bar{\ma} = \lim_{j \to \infty} \ma^{t_j}} is a limit point of \eqn{\{\ma^t\}}. Since \eqn{\{\ma^{t_j}\} \subset \{\ma^t\}} and \eqn{\{f(\ma^{t_j})\} \subset \{f(\ma^t)\}}, it follows from Appendices \ref{c-a} and \ref{mcity} that
\begin{equation} \label{seq_mon}
\dotsc < f(\ma^{t_{j+1}}) < f(\ma^{t_{j}}) < f(\ma^{t_{j-1}}) < \dotsc.
\end{equation}
%Note that the inequality in \eqref{seq_mon} holds while alternating the optimization variables as shown in \eqref{fixed_point}. 
Now, by taking the limit as \eqn{j \to \infty} and by using the continuity of objective function \eqn{f}, we obtain
\begin{equation} \label{limpoint}
\lim_{t \to \infty} f(\ma^{t}) = \lim_{j \to \infty} f(\ma^{t_j}) = f(\lim_{j \to \infty} \ma^{t_{j}}) = f(\bar{\ma}).
\end{equation}

@@

Now, by using strict monotonicity of \eqn{\{f(\ma^{t_j})\}}, it follows that as \eqn{j \to \infty}, \eqn{\ma^{t_j} \to \bar{\ma}} and \eqn{f(\ma^{t_{j}}) - f(\ma^{t_{j+1}}) \to 0}. Moreover, since \eqn{\bar{\ma}} is the solution of \eqref{con-m}, it satisfies \eqref{strict_monotonicity} over convex subset \eqn{\mc{Q}}, which can either be \eqn{\iter{\mc{X}}{k}{i}} or \eqn{\iter{\mc{Y}}{k}{i}} as \eqn{k \to \infty, i \to \infty}. Using the above statements, we can show that \eqn{\bar{\ma}} satisfies the optimality condition  \cite[Prop. 2.1.2]{bertsekas1999nonlinear} as 
\begin{equation} \label{seq_mon1}
\nabla f (\bar{\ma})^\tran (\ma - \bar{\ma}) \geq 0, \; \fall \ma \in \mc{Q} \subset \mc{F} \eqsub.
\end{equation}
Hence, \eqn{\bar{\ma}} is a stationary point and by using \eqref{limpoint}, we can show that every limit point of \eqn{\{\ma^t\}} is a stationary point.

Now to prove that \eqn{\bar{\ma}} is also a stationary point of original nonconvex problem \eqref{con}, we show the equivalence between gradients of subproblem \eqref{con-m} and \eqref{con} at stationary point \eqn{\bar{\ma}}. In order to ensure that \eqn{\bar{\ma}} is a \ac{KKT} point for \eqref{con}, it must satisfy the gradient condition of \eqref{con}, \textit{i.e.},
\begin{equation} \label{kkt_expr}
\textstyle	\nabla \hat{f}(\bar{\ma}) + \mu_0 \big [ \nabla h(\bar{\ma}) - \nabla {g}_0(\bar{\ma}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\bar{\ma}) = 0
\end{equation}
for some Lagrange multipliers \eqn{\mu_i \geq 0} and feasible as \eqn{\bar{\ma} \in \mc{F}}.

>>>>

Using the discussions in Appendices \ref{b_obj} and \ref{mcity}, we can show that the bounded and monotonically decreasing sequence \eqn{\{f(\ma^t)\}} generated by the iterative algorithm converges, using \cite[Prop. A.3]{bertsekas1999nonlinear}. Unfortunately, such a claim cannot be made on the convergence of \eqn{\{\ma^t\}}. However, due to the compactness of feasible set, the sequence of iterates \eqn{\{\ma^t\}} is bounded. Therefore, there exists at least one subsequence that converges to a limit point in the feasible set \cite[Th. 3.6]{rudin1964principles}.

We now show that every limit point of the sequence \eqn{\{\ma^t\}} is a stationary point, \textit{i.e.,} the limit point of every convergent subsequence is a stationary point. To do this, let us consider a subsequence \eqn{\{\ma^{t_j} |j = 0,1,\dotsc\}} of \eqn{\{\ma^t\}} that converges to \eqn{\bar{\ma}}, where \eqn{\bar{\ma} = \lim_{j \to \infty} \ma^{t_j}} is a limit point of \eqn{\{\ma^t\}}. Since \eqn{\{\ma^{t_j}\} \subset \{\ma^t\}} and \eqn{\{f(\ma^{t_j})\} \subset \{f(\ma^t)\}}, it follows from Appendices \ref{c-a} and \ref{mcity} that 
\begin{equation} \label{seq_mon}
f(\ma^{t_{j+1}}) \leq f(\ma^{t_{j}}).
\end{equation}
%Note that the inequality in \eqref{seq_mon} holds while alternating the optimization variables as shown in \eqref{fixed_point}. 
Now, by taking the limit as \eqn{j \to \infty} and by using the continuity of objective function \eqn{f}, we obtain
\begin{equation} \label{limpoint}
\lim_{t \to \infty} f(\ma^{t}) = \lim_{j \to \infty} f(\ma^{t_j}) = f(\lim_{j \to \infty} \ma^{t_{j}}) = f(\bar{\ma}).
\end{equation}

@@

Now, by using strict monotonicity of \eqn{\{f(\ma^{t_j})\}}, it follows that as \eqn{j \to \infty}, \eqn{\ma^{t_j} \to \bar{\ma}} and \eqn{f(\ma^{t_{j}}) - f(\ma^{t_{j+1}}) \to 0}. Moreover, since \eqn{\bar{\ma}} is the solution of \eqref{con-m}, it satisfies \eqref{strict_monotonicity} over convex subset \eqn{\mc{Q}}, which can either be \eqn{\iter{\mc{X}}{k}{i}} or \eqn{\iter{\mc{Y}}{k}{i}} as \eqn{k \to \infty, i \to \infty}. Using the above statements, we can show that \eqn{\bar{\ma}} satisfies the optimality condition  \cite[Prop. 2.1.2]{bertsekas1999nonlinear} as 
\begin{equation} \label{seq_mon1}
\nabla f (\bar{\ma})^\tran (\ma - \bar{\ma}) \geq 0, \; \fall \ma \in \mc{Q} \subset \mc{F} \eqsub.
\end{equation}
\review{Hence, \eqn{\bar{\ma}} is a stationary point and by using \eqref{limpoint}, we can show that every limit point of \eqn{\{\ma^t\}} is a stationary point. Now, we show that \eqn{\{\hat{f}(\ma^t)\}} is also convergent. Since \eqn{\{f(\mat{t}) \}} is monotonically decreasing, let us consider an instant \eqn{t} in which \eqn{\mat{t+1}} is the minimizer of \eqref{con-m}, therefore, we have
\begin{equation} \label{mcity_origfunc}
\hat{f}(\mat{t+1}) + \tau^t \|\mat{t+1} - \mat{t} \| \leq \hat{f}(\mat{t}) + \tau^t \|\mat{t} - \mat{t} \|.
\end{equation}
Moreover, we know that \eqn{\{\hat{f}(\mat{t})\}} is bounded, therefore, by using \cite[Prop. A.3]{bertsekas1999nonlinear}, convergence of \eqn{\{\hat{f}(\ma^t)\}} can be ensured.}

Now to prove that \eqn{\bar{\ma}} is also a stationary point of original problem \eqref{con}, we show the equivalence between gradients of subproblems \eqref{con-m} and \eqref{con} at \eqn{\bar{\ma}}. In order to ensure \eqn{\bar{\ma}} is a \ac{KKT} point of \eqref{con}, it must satisfy the gradient condition of \eqref{con}, \textit{i.e.},
\begin{equation} \label{kkt_expr}
\textstyle	\nabla \hat{f}(\bar{\ma}) + \mu_0 \big [ \nabla h(\bar{\ma}) - \nabla {g}_0(\bar{\ma}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\bar{\ma}) = 0
\end{equation}
for some Lagrange multipliers \eqn{\mu_i \geq 0} and feasible as \eqn{\bar{\ma} \in \mc{F}}.

### 2015-11-19 Report/convergence_distributed.tex
updated

\reviewF{Convergence of primal decomposition and \ac{ADMM} follow the same discussions as in Appendix \ref{sec-3.5}, if in each \ac{SCA} step, the distributed schemes converge to the centralized solution. To show that, let us consider subproblem \eqref{eqn-decent-1} in the \eqn{\ith{k}} \ac{SCA} step, solved in a decentralized manner, by considering a regularized objective as in \eqref{mod_obj}. At first, the convergence of primal decomposition is discussed by using following properties. (i) The feasible set is non-empty and bounded, therefore, each subproblem satisfies the Slater's constraint qualifications. (ii) Due to strong convexity of the objective \eqref{mod_obj} in subproblem, the minimizer is unique. Therefore, by using the above facts, convergence of the primal decomposition algorithm can be ensured as \eqn{j \to \infty} using \cite[Prop. 8.2.6]{bertsekas2003convex} by considering diminishing step size in each subgradient update.}

Now, to show the convergence of \ac{ADMM}, we use the discussion in \cite[Prop. 4.2]{bertsekas1989parallel} and \cite{boyd2011distributed} by writing \eqref{eqn-dual-3} as
\begin{IEEEeqnarray}{rCl} \neqsub
	\underset{\mbf{x} \in \mc{C}_1,\mbf{z} \in \mc{C}_2}{\text{minimize}} &\quad& G(\mbf{x}) + H(\mbf{z}) \eqsub \\
	\text{subject to} &\quad& \mbf{A} \mbf{x} = \mbf{z} \eqsub \label{const-admm}
\end{IEEEeqnarray}
where the constraint in \eqref{const-admm} is identical to that of \eqref{const-admm1} used in the \ac{ADMM} subproblem \eqref{eqn-dual-3}. 
To show the convergence, we rely on the following conditions. (i) \me{G,H} should be convex. (ii) \me{\mc{C}_1,\mc{C}_2} should be a convex set and bounded. (iii) \me{\mbf{A}^\herm \mbf{A}} should be invertible. It is evident from the equality constraints \eqref{const-admm} and \eqref{const-admm1} that \me{\mbf{A} = \mbf{I}}, and therefore it is invertible. Note that the objective functions \me{G,H} include \me{\ell_q} norm and an additional quadratic term as in \eqref{mod_obj}, thereby exhibiting strong convexity. Moreover, the feasible set defined by the constraints of \eqref{eqn-decent-1} is convex and has a nonempty interior. Now, by using \cite[Prop. 4.2]{bertsekas1989parallel}, we can show that the \ac{ADMM} algorithm converges to the centralized solution as \me{j \to \infty} by using diminishing step size in each \ac{ADMM} update as discussed in \cite{boyd2011distributed}. Therefore, if both the primal and \ac{ADMM} approaches are allowed to converge to the centralized solution in each \ac{SCA} step, \reviewF{then every limit point of the sequence generated by the distributed algorithms is a stationary point of \eqref{con}, by following the discussions in Appendix \ref{sec-3.5}.}

@@

However, to avoid the nested iterations, the proposed method performs block update of all variables at once to obtain transmit and receive beamformers for limited number of iterations, thus, achieving improved speed of convergence. Since the optimization variables are updated together, it is theoretically difficult to prove the monotonicity of the objective in each block update. Therefore, the convergence of the sequence of iterates generated by the Algorithm \ref{algo-4} is not guaranteed. Moreover, the objective function used to obtain the iterative algorithm is not strongly convex, and therefore the uniqueness of the iterates is also not guaranteed in each update. Thus, the iterative scheme outlined in Algorithm \ref{algo-4} cannot be guaranteed to find a fixed point to ensure convergence.

>>>>

\reviewF{Convergence of the primal decomposition and the \ac{ADMM} follow the same discussions as in Appendix \ref{sec-3.5}, if in each \ac{SCA} step, the distributed schemes converge to the centralized solution. To show that, let us consider subproblem \eqref{eqn-decent-1} in the \eqn{\ith{k}} \ac{SCA} step, solved by distributed method using a regularized objective as in \eqref{mod_obj}. At first, the convergence of the primal decomposition method is discussed by using following properties. (i) The feasible set is non-empty and bounded, therefore, each subproblem satisfies the Slater's constraint qualifications. (ii) Due to strong convexity of the objective \eqref{mod_obj} in subproblem, the minimizer is unique. \review{Therefore, by using the above facts, as \eqn{j \to \infty}, the convergence of the primal decomposition can be shown using \cite[Prop. 8.2.6]{bertsekas2003convex} for a diminishing step size in each subgradient update.}}

Now, to show the convergence of \ac{ADMM}, we use the discussion in \cite[Prop. 4.2]{bertsekas1989parallel} and \cite{boyd2011distributed} by writing \eqref{eqn-dual-3} as
\begin{IEEEeqnarray}{rCl} \neqsub
	\underset{\mbf{x} \in \mc{C}_1,\mbf{z} \in \mc{C}_2}{\text{minimize}} &\quad& G(\mbf{x}) + H(\mbf{z}) \eqsub \\
	\text{subject to} &\quad& \mbf{A} \mbf{x} = \mbf{z} \eqsub \label{const-admm}
\end{IEEEeqnarray}
where the constraint in \eqref{const-admm} is identical to that of \eqref{const-admm1} used in the \ac{ADMM} subproblem \eqref{eqn-dual-3}. 
To show the convergence, we rely on the following conditions. (i) \me{G,H} should be convex. (ii) \me{\mc{C}_1,\mc{C}_2} should be a convex set and bounded. (iii) \me{\mbf{A}^\herm \mbf{A}} should be invertible. It is evident from the equality constraints \eqref{const-admm} and \eqref{const-admm1} that \me{\mbf{A} = \mbf{I}}, and therefore it is invertible. Note that the objective functions \me{G,H} include \me{\ell_q} norm and an additional quadratic term as in \eqref{mod_obj}, thereby exhibiting strong convexity. Moreover, the feasible set defined by the constraints of \eqref{eqn-decent-1} is convex and has a nonempty interior. Now, by using \cite[Prop. 4.2]{bertsekas1989parallel}, we can show that the \ac{ADMM} algorithm converges to the centralized solution as \me{j \to \infty} by using diminishing step size in each \ac{ADMM} update as discussed in \cite{boyd2011distributed}. Therefore, if both the primal and the \ac{ADMM} methods are allowed to converge to the centralized solution in each \ac{SCA} step, \reviewF{then every limit point of the whole sequence of iterates generated by the distributed algorithms is a stationary point of \eqref{con}, by following the discussions in Appendix \ref{sec-3.5}.}

@@

However, to avoid the nested iterations, the proposed method performs block update of all variables at once to obtain transmit and receive beamformers for limited number of iterations, thus, achieving improved speed of convergence. Since the optimization variables are updated together, it is theoretically difficult to prove the monotonicity of the objective in each block update. Moreover, the objective function used to obtain the iterative algorithm is not strongly convex, and therefore the uniqueness of the iterates is also not guaranteed in each update. Thus, the convergence of iterative scheme outlined in Algorithm \ref{algo-4} cannot be guaranteed.

### 2015-11-19 Report/decomposition_solutions.tex
updated

The decentralization is achieved by decomposing the original convex problem in \eqref{eqn-decent-1} to a parallel subproblems coordinated by either primal or \acl{DD} update. The coupling variables are updated in each iteration by exchanging limited information among the \acp{BS}. Before proceeding further, let \me{\bar{\mbfa{\zeta}}_b} be the vector formed by stacking interference terms \eqref{inter_exp} from the neighboring \acp{BS} to the users of \ac{BS} \me{b} and \me{\hat{\mbfa{\zeta}}_{b}} be the stacked interference terms caused by \ac{BS} \me{b} to all users in the neighboring \acp{BS} \me{\bar{\mc{B}}_b}, represented as
\begin{IEEEeqnarray}{rCl} \neqsub
\bar{\mbfa{\zeta}}_{b} &=& \left [ {\zeta}_{l,k,n,\bar{\mc{B}}_b(1)}, \dotsc, {\zeta}_{l,k,n,\bar{\mc{B}}_b(|\bar{\mc{B}}_b|)} \right]^\tran, \forall k \in \mc{U}_{b} \eqsub \\
\hat{\mbfa{\zeta}}_{b} &=& \left [ {\zeta}_{l,\bar{\mc{U}}_b(1),n,b}, {\zeta}_{l,\bar{\mc{U}}_b(2),n,b}, \dotsc, {\zeta}_{l,\bar{\mc{U}}_b(|\bar{\mc{U}}_b|),n,b} \right]^\tran. \eqsub
\end{IEEEeqnarray}
Let us define the vector \me{\mbfa{\zeta}_b}, formed by stacking the interference terms corresponding to the \ac{BS} \me{b} as
\begin{equation}
\mbfa{\zeta}_{b} = \left [\hat{\mbfa{\zeta}}_{b}^\tran, \bar{\mbfa{\zeta}}_{b}^\tran \right ]^\tran. \label{if_vector}
\end{equation}
Since the decentralization solution is an iterative procedure, we represent the \me{\ith{j}} iteration index as \me{x^{(j)}}. Let \me{\mbfa{\zeta}_{b}(b_k)} denote the interference terms corresponding to \ac{BS} \me{b_k} in \ac{BS} \me{b} as
\begin{equation}
\mbfa{\zeta}_{b}(b_k) = \left [ {\zeta}_{l,\mc{U}_b(1),n,b_k},\dotsc, {\zeta}_{l,\mc{U}_b(|\mc{U}_b|),n,b_k} \right].
\end{equation}

>>>>

The decentralization is achieved by decomposing the original convex problem in \eqref{eqn-decent-1} to a parallel subproblems coordinated by either primal or \acl{DD} update. The coupling variables are updated in each iteration by exchanging limited information among the \acp{BS}. Before proceeding further, let \me{\bar{\mbfa{\zeta}}_b} be the vector formed by stacking interference terms \eqref{inter_exp} from the neighboring \acp{BS} to the users of \ac{BS} \me{b} and \me{\hat{\mbfa{\zeta}}_{b}} be the stacked interference terms caused by \ac{BS} \me{b} to all users in the neighboring \acp{BS} \me{\bar{\mc{B}}_b}, represented for each \eqn{b \in \mc{B}} as
\begin{IEEEeqnarray}{rCl} \neqsub
\bar{\mbfa{\zeta}}_{b} &=& \left [ {\zeta}_{1,\mc{U}_b(1),1,\bar{\mc{B}}_b(1)}, \dotsc, {\zeta}_{L,\mc{U}_b(|\mc{U}_b|),N,\bar{\mc{B}}_b(|\bar{\mc{B}}_b|)} \right]^\tran \eqsub \\
\hat{\mbfa{\zeta}}_{b} &=& \left [ {\zeta}_{1,\bar{\mc{U}}_b(1),1,b}, \dotsc, {\zeta}_{L,\bar{\mc{U}}_b(|\bar{\mc{U}}_b|),N,b} \right]^\tran. \eqsub
\end{IEEEeqnarray}
Let us define the vector \me{\mbfa{\zeta}_b}, formed by stacking the interference terms corresponding to the \ac{BS} \me{b} as
\begin{equation}
\mbfa{\zeta}_{b} = \left [\hat{\mbfa{\zeta}}_{b}^\tran, \bar{\mbfa{\zeta}}_{b}^\tran \right ]^\tran. \label{if_vector}
\end{equation}
Since the decentralization solution is an iterative procedure, we represent the \me{\ith{j}} iteration index as \me{x^{(j)}}. Let \me{\mbfa{\zeta}_{b}(b_k)} denote the interference terms corresponding to \ac{BS} \me{b_k} in \ac{BS} \me{b} as
\begin{equation}
\mbfa{\zeta}_{b}(b_k) = \left [ {\zeta}_{1,\mc{U}_b(1),1,b_k},\dotsc, {\zeta}_{L,\mc{U}_b(|\mc{U}_b|),N,b_k} \right].
\end{equation}

### 2015-11-19 Report/dual_approach.tex
updated

	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \fall users}}

@@

			send precoded downlink pilot with \me{\mbf{m}_{l,k,n}}\;

@@

\reviewF{Assuming that the following conditions are satisfied by the distributed schemes in every \ac{SCA} step, \textit{i.e.}, (i) by ensuring the uniqueness of the minimizer, and (ii) by choosing \eqn{J_{\max}} to be sufficiently large to ensure strict monotonicity of the objective, convergence of the distributed algorithms follow the discussions presented in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}. Moreover, even if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, strict monotonic decrease of the objective sequence is still ensured. The reason is that the \ac{MMSE} receiver is optimal for the fixed transmit precoders obtained after each \ac{SCA} update. However, in practice, to reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for few steps, say, \eqn{J_{\max}}. If so, then the convergence of the sequence of iterates generated by the distributed algorithm is not guaranteed, since it is difficult to show the monotonicity of objective in each \ac{SCA} step. The reason is that in each primal or \ac{ADMM} update, the global objective need not be decreasing monotonically.}

>>>>

	\KwOut{\me{\mvec{m}{l,k,n}} and \me{\mvec{w}{l,k,n} \forall l,k,n}}

@@

@@

\reviewF{Assuming that the following conditions are satisfied by the distributed schemes in every \ac{SCA} step, \textit{i.e.}, (i) by ensuring the uniqueness of the minimizer, and (ii) by choosing \eqn{J_{\max}} to be sufficiently large enough to ensure strict monotonicity of the objective, convergence of the distributed algorithms follow the discussions presented in Appendices \ref{sec-3.5} and \ref{sec-dist-conv}. Moreover, if the receivers are updated together with the transmit precoders as in Algorithm \ref{algo-3}, strict monotonic decrease of the objective sequence can still be ensured. The reason is that the \ac{MMSE} receiver is optimal for the fixed transmit precoders obtained after each \ac{SCA} update. However, in practice, to reduce the amount of information exchange among the coupling \acp{BS}, often distributed schemes are iterated for few number of iterations, say, for \eqn{J_{\max}} only. In such a case, the convergence of the sequence of iterates generated by the distributed algorithm cannot not be guaranteed, since it is difficult to show the monotonicity of objective in each \ac{SCA} step. The reason is that in each primal or \ac{ADMM} update, the global objective need not be decreasing monotonically.}

### 2015-11-19 Report/introduction.tex
updated

%The last mile wireless connectivity poses significant bottleneck in the overall data traffic for the interconnected networks. The main challenges in the wireless networks are due to the scarcity of the available resources either in terms of power or spectrum usage and the complexity of the receiver algorithms which impacts the mobile battery consumption. In order to overcome the receiver complexity, \ac{OFDM} is introduced for the wide band transmissions. To improve data rate, multiple antennas are installed at \acp{BS} and/or at user terminals to avail additional freedom in the form of spatial dimension. The inclusion of \ac{MIMO} technique in wireless networks provides higher data rate or lower outage for the same transmission power and bandwidth.
In a network with multiple \acp{BS} serving multiple users, the main driving factor for the transmission is the packets waiting at each \ac{BS} corresponding to the different users existing in the network. We consider the problem of transmit precoder design over the space-frequency resources provided by the \ac{MIMO} \ac{OFDM} framework in the downlink \ac{IBC} to minimize the number of queued packets in the \acp{BS}. Since the resources are shared by multiple users associated with different \acp{BS}, the problem of interest can be viewed as a resource allocation one.

In general, the resource allocation problems such as admission control ones can be formulated by assigning a binary variable for each user to indicate the presence or absence of a particular resource \cite{admission_control}. Alternatively, linear transmit precoders, which are complex vectors, can be implicitly modeled as decision variables, thereby avoiding the use of binary decision variables. After the design stage, the non-zero precoders are used to determine the transmission rates of users on a space-frequency resource, and the zero transmit precoder indicates the absence of the user on a given resource. In this way, the soft decisions are used in the optimization problem and the hard decisions are made after the algorithm convergence.
%The queue minimizing network optimization objective is used to design the beamformers across the coordinating \acp{BS}, since the transmissions are guided by the available backlogged packets. To achieve the best performance, we propose a joint resource allocation scheme over the space and frequency dimensions among the coordinating \acp{BS} to minimize the time that the packets stay in the queues prior to the transmission, and, hence, to avoid packet drops as an indirect objective.

@@

The relation between the achievable sum rate and the \ac{MSE} of the received symbol by using fixed \ac{MMSE} receivers can also be used to solve the \ac{WSRM} problem \cite{mse_duality}. In \cite{christensen2008weighted,wmmse_shi}, the \ac{WSRM} problem is reformulated via \ac{MSE}, casting the problem as a convex one for fixed linearization coefficients. In this way, the original problem is expressed in terms of the \ac{MSE} weight, precoders, and receivers. Then the problem is solved using an alternating optimization method, i.e., finding a subset of variables while the other variables are fixed. The \ac{MSE} reformulation for the \ac{WSRM} problem was also studied in \cite{hong2012decomposition} by using \ac{SCA} to solve the problem in an iterative manner. Moreover, distributed precoder designs with \ac{QoS} requirements as additional rate constraints are studied for the \ac{MSE} reformulated \ac{WSRM} problem in \cite{kaleva2013decentralized}.

>>>>

%The last mile wireless connectivity poses significant bottleneck in the overall data traffic for the interconnected networks. The main challenges in the wireless networks are due to the scarcity of the available resources either in terms of power or spectrum usage and the complexity of the receiver algorithms which impacts the mobile battery consumption. In order to overcome the receiver complexity, \ac{OFDM} is introduced for the wide band transmissions. To improve data rate, multiple antennas are installed at \acp{BS} and/or at user terminals to avail additional freedom in the form of spatial dimension. The inclusion of \ac{MIMO} technique in wireless networks provides higher data rate or lower outage for the same transmission power and bandwidth.
In a network with multiple \acp{BS} serving multiple users, the main driving factor for the transmission is the packets waiting at each \ac{BS} corresponding to the different users existing in the network. We consider the problem of transmit precoder design and resource allocation over the space-frequency resources provided by the \ac{MIMO} \ac{OFDM} framework in the downlink \ac{IBC} to minimize the number of queued packets in the \acp{BS}. Thus, the problem of interest inherently includes resource allocation of users associated with different \acp{BS}.

In general, the resource allocation problems such as admission control can be formulated by assigning a binary variable for each user to indicate the presence or absence of a particular resource \cite{admission_control}. Alternatively, linear transmit precoders, which are complex vectors, can be implicitly modeled as decision variables, thereby avoiding the use of binary decision variables. After the design stage, the non-zero precoders are used to determine the transmission rates of users on a space-frequency resource, and the zero transmit precoder indicates the absence of the user on a given resource. In this way, the soft decisions are used in the optimization problem and the hard decisions are made after the algorithm convergence.
%The queue minimizing network optimization objective is used to design the beamformers across the coordinating \acp{BS}, since the transmissions are guided by the available backlogged packets. To achieve the best performance, we propose a joint resource allocation scheme over the space and frequency dimensions among the coordinating \acp{BS} to minimize the time that the packets stay in the queues prior to the transmission, and, hence, to avoid packet drops as an indirect objective.

@@

The relation between the achievable sum rate and the \ac{MSE} of the received symbol by using fixed \ac{MMSE} receivers can also be used to solve the \ac{WSRM} problem \cite{mse_duality}. In \cite{christensen2008weighted,wmmse_shi}, the \ac{WSRM} problem is reformulated via \ac{MSE}, casting the problem as a convex one for fixed linearization coefficients. In this way, the original problem is expressed in terms of the \ac{MSE} weight, precoders, and receivers. Then the problem is solved using an alternating optimization method, i.e., finding a subset of variables while the other variables are fixed. The \ac{MSE} reformulation for the \ac{WSRM} problem was also studied in \cite{kaleva2012weighted} by using \ac{SCA} to solve the problem in an iterative manner. Moreover, distributed precoder designs with \ac{QoS} requirements as additional rate constraints are studied for the \ac{MSE} reformulated \ac{WSRM} problem in \cite{kaleva2013decentralized}.
